---
title: "Covid91 vaccine study Final2023"
author: "Th3b0yn3xtd00r"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "Summer 2023" 
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
FinalData <-read.csv(file="final.csv",header=TRUE)
#recode to remove the annoying "X" from the dataframe
FinalData <- FinalData  %>% select(-one_of("X"))
FinalData <- FinalData %>%
mutate(across(where(is.character), as.factor))
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(knitr)
data(FinalData)
FinalData <- na.omit(FinalData)
```

# Introduction

A new  preventative vaccine (Covid-19) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of sub populations tracked. Consider population subgroups by gender(males and females), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine. Structure your report in four sections each devoted to one of the four subgroups, use null and alternative hypothesis statements and correct statistical verbiage when referencing p-values in conclusions.

## Males
### Introduction

The new preventative vaccine for (Covid 19) is being used to see if the vaccine has any effect on the Males and whether it prevents the Diesease Covid-19 against those who do not take the vaccine.

### Methods

The methods we are using to approach this hypothesis are the bar plots to graph the data, a Table test for numerical data for the exact numbers, and an Chi test/Fisher XY test for Inferential data. While using our CAT~CAT helper file for our variable analysis, making the Males, Females, LGBTQ, and Druggies for Categorical as well as the Vaccine for Covid also being Categorical.

$H_0$ There is no difference in the effect the vaccine has on Males and does not prevent Covid-19

$H_A$ There is a difference in the effect the vaccine has on Males and does prevent Covid-19.

### Results

#### Descriptive Results

##### Graphical Results

```{r}
barchartGC(~class + Sex,data=ucdavis1)
barchartGC(~class + Sex,data=ucdavis1, type="percent")

```


##### Numerical Results
Chunk + description

##### Inferential Results
Chunk + description

### Disscussion and Conclusion
Description



## Females
### Introduction

### Methods

### Results
Chunk?
#### Descriptive Results

##### Graphical Results
Chunk + description

##### Numerical Results
Chunk + description

##### Inferential Results
Chunk + description

### Disscussion and Conclusion
Description



## LGBTQ
### Introduction

### Methods

### Results
Chunk?
#### Descriptive Results

##### Graphical Results
Chunk + description

##### Numerical Results
Chunk + description

##### Inferential Results
Chunk + description

### Disscussion and Conclusion
Description



## Druggies
### Introduction

### Methods

### Results
Chunk?
#### Descriptive Results

##### Graphical Results
Chunk + description

##### Numerical Results
Chunk + description

##### Inferential Results
Chunk + description

### Disscussion and Conclusion
Description


# Overall Results and Conclusions
Description covering all four each separately and then all four together whether they should take the vaccine.